---
title: "Lab 8 - IMDB Top 250"
author: "Annie Hou"
date: "03/26/2024"
output: html_document
---


### Load packages

```{r load-packages, message = FALSE}
library(tidyverse)
library(rvest)
```


### Exercise 1

```{r}
url <- "https://www.imdb.com/chart/top"
page <- read_html(url)
```


### Exercise 2

The class is xml_document and xml_node.

```{r ex2}
class(page)
```


### Exercise 3

```{r ex3}
titles <- page %>% 
    html_nodes(".ipc-title__text") %>% 
    html_text()
```

### Exercise 4

The top 10 are not all titles of the movies; it includes the general titles for the IMDb charts.

```{r ex4}
print(head(titles,10))
```


### Exercise 5

The last 10 are not actural movie titles - those are the contents in the bottom of the page.

```{r ex5}
print(tail(titles,10))
```

### Exercise 6

```{r ex6}
titles <- str_subset(titles, "^[0123456789]")
```

### Exercise 7

Now, the length of the vector is 250.

```{r ex7}
print(length(titles))
```

### Exercise 8

```{r ex8}
titles <-str_remove(titles, "^[0123456789]+\\. ")
print(head(titles,10))
```

### Exercise 9

```{r ex9}
years <- page %>%
  html_nodes(".cli-title-metadata span:nth-child(1)") %>%
  html_text() %>%
  as.numeric()

print(head(years, 10))
```


### Exercise 10

```{r ex10}
ratings <- page %>%
  html_nodes(".ipc-rating-star--imdb") %>%
  html_attr("aria-label") %>%
  str_sub(-3, -1) %>%
  as.numeric()

print(head(ratings, 10))
```

### Exercise 11

```{r ex11}
imdb_top_250 <- data.frame(
  title = titles,
  year = years,
  rating = ratings
)

# print(imdb_top_250)
```

### Exercise 12

```{r ex12}
imdb_top_250 <- imdb_top_250 %>%
  mutate(rank = 1:nrow(imdb_top_250))

head(imdb_top_250, 5)
```

### Exercise 13

```{r ex13}
ggplot(imdb_top_250, aes(x = year, y = rating)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  
  theme_minimal() +  
  labs(title = "IMDb Top 250 Movies Ratings Over Time",
       x = "Year",
       y = "Rating")
```

